\section{Chapter 9}
\begin{center}
    %{\scshape\Large Chapter 9}\\
    {\large Section A}
\end{center}

\doublespace

\noindent
\makebox[0.8\linewidth]{Who is this man?  \dotfill}\\[0.1in]
\makebox[0.8\linewidth]{He is Abbas.\dotfill}\\[0.1in] 
\makebox[0.8\linewidth]{Abbas is a merchant. \dotfill}\\[0.1in]
\makebox[0.8\linewidth]{Hamid is a teacher.  \dotfill}\\[0.1in]
\makebox[0.8\linewidth]{Hamid is a new teacher. \dotfill}\\[0.1in] 
\makebox[0.8\linewidth]{What is this?  \dotfill}\\[0.1in]
\makebox[0.8\linewidth]{This is an apple. \dotfill}\\[0.1in]
\makebox[0.8\linewidth]{The apple is a delicious \hl{\textbf{fruit}}. \dotfill}\\[0.1in]
\makebox[0.8\linewidth]{What is that?  \dotfill}\\[0.1in]
\makebox[0.8\linewidth]{That is a \hl{\textbf{sparrow}}. \dotfill}\\[0.1in]
\makebox[0.8\linewidth]{The sparrow is a small \hl{\textbf{bird}}. \dotfill}\\[0.1in]
\makebox[0.8\linewidth]{Arabic \hl{\textbf{language}} is \hl{\textbf{easy}}.  \dotfill}\\[0.1in]
\makebox[0.8\linewidth]{Arabic language is beautiful.  \dotfill}\\[0.1in]
Ammar is a \hl{\textbf{hardworking}} student, and Mahmood is a \hl{\textbf{lazy}} student.\\[0.1in] \answerline \\[0.25in]
\makebox[0.8\linewidth]{Who are you?  \dotfill}\\[0.1in]
\makebox[0.8\linewidth]{I am a student.  \dotfill}\\[0.1in]
\makebox[0.8\linewidth]{Are you a new student?  \dotfill}\\[0.1in]
\makebox[0.8\linewidth]{Yes, I am a new student.  \dotfill}\\[0.1in]

\subsection{Exercise 1}
Translate
\begin{enumerate}
    \item Mohammed is an old student. \\[0.1in] \answerline 
    \item Is this man a new teacher? No, he is a new student. \\[0.1in] \answerline 
    \item This lesson is easy. \\[0.1in] \answerline 
    \item Abbas is a \hl{\textbf{famous}} merchant.  \\[0.1in] \answerline 
    \item Bilal is a big engineer. \\[0.1in] \answerline 
    \item English is a difficult language. \\[0.1in] \answerline 
    \item Are you a rich man? No, I am a poor man.  \\[0.1in] \answerline 
    \item \hl{\textbf{Cairo}} is a big city.  \\[0.1in] \answerline
    \item Are you an old teacher? No I am a new teacher. \\[0.1in] \answerline
    \item Is Hamid a lazy student? No, he is a hardworking student.  \\[0.1in] \answerline
    
\end{enumerate}

\subsection{Exercise 2}
Fill with appropriate adjective and complete the sentence in Arabic.
\begin{enumerate}
    \item Khadija is a \fillin student. \\[0.1in] \answerline
    \item Khalid is a \fillin merchant. \\[0.1in] \answerline
    \item Arabic is a \fillin language. \\[0.1in] \answerline
    \item The sparrow is a \fillin bird. \\[0.1in] \answerline
    \item The apple is a \fillin fruit. \\[0.1in] \answerline
    \item I am a \fillin teacher.  \\[0.1in] \answerline
    \item Muhammad is a \fillin student. \\[0.1in] \answerline
    \item English is a \fillin language.  \\[0.1in] \answerline
    \item Are you a \fillin student?  \\[0.1in] \answerline
    \item Cario is a \fillin city. \\[0.1in] \answerline
\end{enumerate}

\subsection{Exercise 3}
Fill in with appropriate noun to complete the sentence. Then translate it in Arabic below. 
\begin{enumerate}
    \item Arabic is an easy \fillin.  \\[0.1in] \answerline 
    \item I am an old \fillin. \\[0.1in] \answerline 
    \item Ammar is a rich \fillin. \\[0.1in] \answerline 
    \item This is a broken \fillin. \\[0.1in] \answerline 
    \item Faisal is a lazy \fillin. \\[0.1in] \answerline 
\end{enumerate}

\subsection{Exercise 4}
Translate the following sentences. 
\begin{enumerate}
    \item I am hungry.  \\[0.1in] \answerline 
    \item Are you hungry? No I am \hl{\textbf{thirsty}}. \\[0.1in] \answerline 
    \item Why is the teacher angry \hl{\textbf{today}}?  \\[0.1in] \answerline 
    \item The \hl{\textbf{cup}} is full. \\[0.1in] \answerline 
\end{enumerate}


\subsection{New Vocab}
\begin{itemize}
    \item \makebox[0.5\linewidth]{The language \dotfill}
    \item \makebox[0.5\linewidth]{Famous \dotfill}
    \item \makebox[0.5\linewidth]{The city \dotfill}
    \item \makebox[0.5\linewidth]{The bird \dotfill}
    \item \makebox[0.5\linewidth]{Today \dotfill}
    \item \makebox[0.5\linewidth]{Lazy \dotfill}
    \item \makebox[0.5\linewidth]{Hungry \dotfill}
    \item \makebox[0.5\linewidth]{Thirsty \dotfill}
    \item \makebox[0.5\linewidth]{Full  \dotfill}
    \item \makebox[0.5\linewidth]{Angry \dotfill}
    \item \makebox[0.5\linewidth]{The sparrow \dotfill}
\end{itemize}