\pagebreak
\section{Chapter 8}
\doublespace

This man is a merchant and that man is a doctor. \\[0.1in]\answerline\\ 
The Merchant's name is Muhammad and the doctor's name is Saeed. \\[0.1in]\answerline\\ 
This house belongs to the merchant and that house belongs to the doctor. \\[0.1in]\answerline\\ 
The merchant's house is in front of the masjid and the doctor's house is behind the school. \\[0.1in]\answerline\\ 
Whose car is this and whose is that? \\[0.1in]\answerline\\ 
This car belongs to the doctor and that belongs to the merchant. \\[0.1in]\answerline\\ 
This car is from Japan and that is from America. \\[0.1in]\answerline\\ 

\subsection{Translate}
\begin{enumerate}
    \item Who is this man and who is that man? \\[0.1in]\answerline
    \item What is the merchant's name? \\[0.1in]\answerline
    \item what is the doctor's name? \\[0.1in]\answerline
    \item Where is the doctor's car from? \\[0.1in]\answerline
    \item Where is the merchant's car from? \\[0.1in]\answerline
    \item Where is the merchant's house? \\[0.1in]\answerline
    \item Where s the doctor's house? \\[0.1in]\answerline
\end{enumerate}
\pagebreak
\subsection{Iqra waktabu}
\begin{enumerate}
    \item This boy is Khalid and that boy is Muhammad. \\[0.1in] \answerline
    \item This man is a teacher and that man is an engineer. \\[0.1in] \answerline
    \item This book is new and that book is old. \\[0.1in] \answerline
    \item This car belongs to Ali and that belongs to Khalid.\\[0.1in] \answerline
    \item This door is open and that door is closed. \\[0.1in] \answerline
    \item To whom does this watch belong to? It belongs to Abbas. \\[0.1in] \answerline
    \item Does this house belong to the doctor? No, it belongs to the teacher. \\[0.1in] \answerline
    \item Does this cycle belong to the muazzin's son? Yes.  \\[0.1in] \answerline
    \item Who is this boy? He is a student from Iraq. \\[0.1in] \answerline
    \item Is this house new? No, It is very old.  \\[0.1in] \answerline
    \item This car is from Japan and that from Switzerland.  \\[0.1in] \answerline
    \item This \hl{\textbf{knife}} is from Germany and that spoon is from \hl{\textbf{England}} \\[0.1in] \answerline
\end{enumerate}

\subsection{Something}
\begin{enumerate}
    \item This is a doctor \dotfill \\[0.1in]This doctor is from India. \dotfill
    \item This is a car. \dotfill \\[0.1in]This car belongs to the principal. \dotfill
    \item That is a boy \dotfill \\[0.1in]That boy is the teacher's son. \dotfill
    \item That is a watch \dotfill \\[0.1in]That watch is from Switzerland. \dotfill
    \item This is a house \dotfill \\[0.1in]This house belongs to the engineer. \dotfill
    \item This is a pen \dotfill \\[0.1in]This pen belongs to Abbas. \dotfill
    \item That is a man \dotfill \\[0.1in]That man is a muazzin. \dotfill
    \item This is an egg \dotfill \\[0.1in]This egg is big. \dotfill
    \item This is a handkerchief \dotfill \\[0.1in]This handkerchief is dirty. \dotfill
    \item This is a bag \dotfill \\[0.1in]This bag belongs to the teacher. \dotfill
\end{enumerate}

\subsection{Translate again}
\begin{enumerate}
    \item Whose pen is this? \dotfill \\[0.1in]This pen belongs to Abbas \dotfill
    \item Whose key is this? \dotfill \\[0.1in]This key belongs to Ali. \dotfill
    \item Whose car is this? \dotfill \\[0.1in]This car belongs to the principal \dotfill
    \item Whose cow is this? \dotfill \\[0.1in]This cow belongs to the farmer. \dotfill
    \item Whose bag is this? \dotfill \\[0.1in]This bag belongs to the teacher \dotfill
    \item Whose chair is this? \dotfill \\[0.1in]This chair belongs to Ammar \dotfill
    \item Whose rooster is this? \dotfill \\[0.1in]This rooster belongs to the farmer's daughter \dotfill
    \item Whose watch is this? \dotfill \\[0.1in]This watch belongs to the principal's son \dotfill
    \item Whose house is this? \dotfill \\[0.1in]This house belongs to the doctor. \dotfill
    \item Whose spoon is this? \dotfill \\[0.1in]This spoon belongs to the student \dotfill
\end{enumerate}

\subsection{Harf ul jarr endings}
\begin{enumerate}
    \item House
    \begin{itemize}
        \item The house \dotfill
        \item In the house \dotfill
        \item From the house \dotfill
        \item To the house \dotfill
    \end{itemize}
    \item \hl{\textbf{Hospital}}
    \begin{itemize}
        \item The hospital \dotfill
        \item In the hospital \dotfill
        \item From the hospital \dotfill
        \item To the hospital \dotfill
    \end{itemize}
    \item America
    \begin{itemize}
        \item America \dotfill
        \item In America \dotfill
        \item From America \dotfill
        \item To America \dotfill
    \end{itemize}
    \item Germany
    \begin{itemize}
        \item Germany \dotfill
        \item In Germany \dotfill
        \item From Germany \dotfill
        \item To Germany \dotfill
    \end{itemize}
    
\end{enumerate}

\subsection{Translate again}
\begin{itemize}
    \item This doctor is from England  \\[0.1in]\answerline
    \item Hamid went to \hl{\textbf{France}} \\[0.1in]\answerline
    
    \item Muhammad is sick. He is now in the hospital. \\[0.1in]\answerline
    \item Abdullah went from Germany to England.  \\[0.1in]\answerline
    \item This book belongs to Abbas, and that book belongs to \hl{\textbf{Musa}} \\[0.1in]\answerline
    \item This engineer is from America. \\[0.1in]\answerline
\end{itemize}

\subsection{Translate again}
\begin{itemize}
    \item The blackboard is in front of the student and she is behind the teacher. \\[0.1in]\answerline
    \item Where is the teacher's car? It is in front of the school. \\[0.1in]\answerline
    \item Where is the imaam's house? The imaam's house is behind the masjid. \\[0.1in]\answerline
    \item Where did Hamid sit? He said behind Muhammad. \\[0.1in]\answerline
    \item Ammar went to the masjid and sat in front of the mihrab. \\[0.1in]\answerline
\end{itemize}